\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2013-09-06 paper.tex
Fixed my terrible compilation issue
Was only a question of correct ordering of 'frontmatter' and 'document'. My bad.
Modify coauthors + acknowledgments according to Rachid's wishes

\usepackage[english]{babel}
\usepackage{cite}
\usepackage{graphicx, subfigure}

@@

\begin{frontmatter}

@@

\author{Séverin Lemaignan, Rachid Alami}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{abstract}

@@

Building such a robotic architecture is the work of many hands, and we would
like to acknowledge here the worthwhile contributions of Aurélie Clodic, Mamoun
Gharbi, Julien Guitton, Matthieu Herrb, Jim Mainprice, Amit Kumar Pandey and
Mathieu Warnier.

>>>>

\usepackage[english]{babel}
\usepackage{graphicx, subfigure}

@@

\begin{document}
\begin{frontmatter}

@@

\author{Séverin Lemaignan, Mathieu Warnier, E. Akin Sisbot, Rachid Alami}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

@@

Building such a robotic architecture is the work of many hands, and we would
like to acknowledge here the worthwhile contributions of Samir Alili, Aurélie
Clodic, Raquel Ros Espinoza, Mamoun Gharbi, Julien Guitton, Matthieu Herrb, Jim
Mainprice and Amit Kumar Pandey.
